---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LRM

<!-- badges: start -->
[![R-CMD-check](https://github.com/Flora843/biostat625hw3/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Flora843/biostat625hw3/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Flora843/biostat625hw3/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Flora843/biostat625hw3?branch=main)
<!-- badges: end -->


## Introduction

### *What is "LRM"?*

This R package helps users to fit a linear regression model. It calculate coefficients and carry out some important tests of the existing `stats::lm` function. Besides, it can calculate the confidence interval of estimated beta and obtain the covariance matrix. However, it can't fit a model without an intercept properly. It can't explore the interaction between predictors. 

### *What users can obtain with "LRM"?*

Here are some results that the users can obtain using `LRM` package:

* Get the point estimates and standard errors of $\hat{\beta}$
* Obtain the $t$-statistics and the corresponding p value.
* Get the confidence interval of $\hat{\beta}$
* Get the $R^2$ and adjusted-$R^2$.
* Obtain the $F$-statistics
* Get covariance matrix of estimated coefficients


## Installation

You can install the development version of LRM from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Flora843/biostat625hw3")
```


## Example

This is an example：

```{r example}
library(LRM)
LRM(mpg~wt+drat,data=mtcars)$LRM_coefs
LRM(mpg~wt+drat,data=mtcars)$F.statistics
LRM(mpg~wt+drat,data=mtcars)$R.squared
LRM(mpg~wt+drat,data=mtcars)$Confidence.Interval
LRM(mpg~wt+drat,data=mtcars)$covariance.matrix
```





