---
title: "Package:LRM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(LRM)
library(bench)
```

## Introduction

### *(1).What is "LRM"?*

This is a function that help users to fit a linear regression model

[Linear Regression](https://www.ibm.com/topics/linear-regression) 

Linear regression is a linear method for modelling the relationship between a response variable and one or multiple explanatory variables. It is applied for predicting, forecasting or evaluating the strength of the relationship between the response and the explanatory variables.

### *(2).What can "LRM" package do?*

This R package can calculate some coefficients and carry out some important tests of the existing `stats::lm` function. However, it can't fit a model without an intercept properly. It can't explore the interaction between predictors. 

Here are some results that the users can obtain using `LRM` package:

* Get the point estimates and standard errors of estimated coefficients
* Obtain T statistics and the corresponding p value.
* Get the confidence interval of estimated coefficients
* Get the R squared and adjusted R squared value
* Obtain  F statistics
* Get covariance matrix of estimated coefficients


## Installation

* Please download `LRM` from github

  ```
  # install.packages("devtools")
  devtools::install_github("Flora843/biostat625hw3")
  ```
  
## Loading packages

```
library(LRM)
```

## Details about how to use "LRM"
  
* **formula**: y ~ x  
y: response variable
x: explanatory variables (It is likely to fit more than one variables)

* **data** : A numerical data frame

* **alpha** : significance value(default=0.05)

Let's look at some examples:

We will use the `"mtcars"` data

*(1) Fit a simple linear regression model:*
```{r}
SLR=LRM(mpg~wt,data=mtcars,alpha=0.05)
#To obtain coefficient table 
print(SLR$LRM_coefs)
#To obtain R.squared and Adjusted R.squared
print(SLR$R.squared)
# To obtain F statistics 
print(SLR$F.statistics)
# To obtain confidence interval
print(SLR$Confidence.Interval)
# To obtain covariance matrix
print(SLR$covariance.matrix)
```

*(2) Fit a multiple linear regression model:*
```{r}
MLR=LRM(mpg~wt+drat+hp,data=mtcars,alpha=0.02)
#To obtain coefficient table 
print(MLR$LRM_coefs)
#To obtain R.squared and Adjusted R.squared
print(MLR$R.squared)
# To obtain F statistics 
print(MLR$F.statistics)
# To obtain confidence interval
print(MLR$Confidence.Interval)
# To obtain covariance interval
print(MLR$covariance.matrix)
```
```
## Correctness

**(1) Compare the point estimate and standard error of $\hat{\beta}$ **
```{r}
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$LRM_coefs[,1]),
         as.vector(summary(lm(mpg~wt+drat,data=mtcars))$coefficients[,1]))
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$LRM_coefs[,2]),
         as.vector(summary(lm(mpg~wt+drat,data=mtcars))$coefficients[,2]))
```

**(2)Compare Confidence interval**
```{r}
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$Confidence.Interval[1,1]),
         as.vector(confint(lm(mpg~wt+drat,data=mtcars))[1,1]))
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$Confidence.Interval[1,2]),
         as.vector(confint(lm(mpg~wt+drat,data=mtcars))[1,2]))
```

**(3)Compare adjusted R Squared **
```{r}
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$R.squared$Adjusted.R.squared),
          as.vector(summary(lm(mpg~wt+drat,data=mtcars))$adj.r.squared))
```

**(4)Compare F statistics **

```{r}
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$F.statistics$value),
          as.vector(summary(lm(mpg~wt+drat,data=mtcars))$fstatistic[1]))

```

**(4)Compare t statistics and p value **

```{r}
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$LRM_coefs[,3]),
        as.vector(summary(lm(mpg~wt+drat,data=mtcars))$coefficients[,3]))
all.equal(as.vector(LRM(mpg~wt+drat,data=mtcars)$LRM_coefs[,4]),
        as.vector(summary(lm(mpg~wt+drat,data=mtcars))$coefficients[,4]))
```

**(5)Compare t statistics and p value **
There is no function that could directly calculate covariance of estimated coefficients.


## Efficiency
```{r}
efficiency_cpr <-bench::mark(LRM = {
  betahat.actual <-LRM(mpg~wt+drat,data=mtcars)$LRM_coefs[, 1]
  as.vector(betahat.actual)
}, lm_summary = {
  betahat.expected <-lm(mpg~wt+drat,data=mtcars)$coefficients
  as.vector(betahat.expected)
})  
summary(efficiency_cpr)
itr.sec <- as.numeric(efficiency_cpr[[4]])
print(itr.sec)
total.time<-as.numeric(efficiency_cpr[[9]])
print(total.time)
```
It was observed that the 'LRM' model is more efficient than 'lm'. 'LRM' has less number of executions performed per second and shorter total time.

