---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LRM)
```

## Introduction

### *(1).What is "LRM"?*

[Linear Regression](https://www.ibm.com/topics/linear-regression) 

### *(2).What can "LRM" package do?*

This R package can calculate some coefficients and carry out some important tests of the existing `stats::lm` function. Besides, this package can calculate the confidence interval of estimated beta

Here are some results that the users can obtain using `LRM` package:

* Fit a linear regression model.
* Get the point estimates and standard errors of $\hat{\beta}$
* Obtain the $t$-statistics and the corresponding p value.
* Get the confidence interval of $\hat{\beta}$
* Get the $R^2$ and adjusted-$R^2$.
* Obtain the $F$-statistics

## Installation

* `LRM` can be downloaded from github now

  ```
  # install.packages("devtools")
  devtools::install_github("Flora843/biostat625hw3")
  ```

